A Partitioning Algorithm for Maximum Common Subgraphs\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/K503058/1 and EP/M508056/1]}

### 2017-02-14 paper/paper.tex
Added some subfigures

@@

\begin{figure}
    \centering
    \includegraphics*{gen-graph-plain-cumulative.pdf}
    \caption{MCS Plain instances, cumulative runtimes}\label{figure:plain-cumulative}
\end{figure}

%\begin{figure}
%    \centering
%    \includegraphics*{gen-graph-33v-cumulative.pdf}
%    \caption{MCS 33\% vertex labelled, no edge labels, undirected instances, cumulative runtimes}\label{figure:33v-cumulative}
%\end{figure}
%
%\begin{figure}
%    \centering
%    \includegraphics*{gen-graph-33ve-cumulative.pdf}
%    \caption{MCS 33\% vertex and edge labelled undirected instances, cumulative runtimes}\label{figure:33ve-cumulative}
%\end{figure}

\begin{figure}
    \centering
    \includegraphics*{gen-graph-33ved-cumulative.pdf}
    \caption{MCS 33\% vertex and edge labelled directed instances, cumulative runtimes}\label{figure:33ved-cumulative}
\end{figure}

\begin{figure}
    \centering
    \includegraphics*{gen-graph-plain-connected-cumulative.pdf}
    \caption{Unlabelled undirected instances, connected, cumulative runtimes}\label{figure:plain-connected-cumulative}
\end{figure}

\begin{figure}
    \centering
    \includegraphics*{gen-graph-33ve-connected-cumulative.pdf}
    \caption{MCS 33\% vertex and edge labelled undirected instances, connected, cumulative runtimes}\label{figure:33ve-connected-cumulative}
\end{figure}

\begin{figure}
    \centering
    \includegraphics*{gen-graph-sip-cumulative.pdf}
    \caption{SIP instances, cumulative runtimes}\label{figure:sip-cumulative}
\end{figure}

>>>>

\usepackage{subfigure}

@@

\begin{figure}
    \centering
    \subfigure[][MCS unlabelled unconnected instances] {
        \centering
        \includegraphics*{gen-graph-plain-cumulative.pdf}
        \label{figure:plain-cumulative}
    }

    \subfigure[][MCS 33\% vertex and edge labelled directed instances] {
        \centering
        \includegraphics*{gen-graph-33ved-cumulative.pdf}
        \label{figure:33ved-cumulative}
    }
    \caption{Cumulative runtimes}\label{figure:mcs-cumulative}
\end{figure}

\begin{figure}
    \centering
    \subfigure[][MCS unlabelled undirected instances] {
        \centering
        \includegraphics*{gen-graph-plain-connected-cumulative.pdf}
        \label{figure:plain-connected-cumulative}
    }

    \subfigure[][MCS 33\% vertex and edge labelled undirected instances] {
        \centering
        \includegraphics*{gen-graph-33ve-connected-cumulative.pdf}
        \label{figure:33ve-connected-cumulative}
    }
    \caption{Cumulative runtimes, connected variant}
    \label{figure:mcs-connected-cumulative}
\end{figure}

\begin{figure}
    \centering
    \includegraphics*{gen-graph-sip-cumulative.pdf}
    \caption{Cumulative runtimes, SIP instances}\label{figure:sip-cumulative}
\end{figure}
